Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-18 analysis/paper/paper.Rmd
Edit to schematic figure caption

```{r, schematic-figure, fig.cap="Schematic figure showing both the intial measurements that were used to generate our landmarks and the location of our landmarks on a hypothetical flake. A, B, C, D, and E are the top horizontal measurement, width at a quarter of the maximum length, maximum dimension length, width at a quarter of the maximum length, and width at three quarter of the maximum length respectively. Points 1 through 9 are all of the landmarks generated from measurements A through E."}
knitr::include_graphics(here::here("analysis/figures/flake-measurements-schematic-figure-temp.png"))
```

>>>>

```{r, schematic-figure, fig.cap="Schematic figure showing the location of our landmarks on a hypothetical flake"}
knitr::include_graphics(here::here("analysis/figures/flake-measurements-schematic-figure-temp.png"))
```
